A Loop Quantum Gravity Inspired Action for the Bosonic String and Emergent Dimensions at Large Scales

### 2025-09-07 AoP/resubmit-cover-letter-r2.tex
Complete T4: Submit final AOP manuscript revisions
- Enhanced Kalb-Ramond field derivation with step-by-step exposition
- Fixed equation label references for improved clarity
- Addressed all referee clarifications in response document
- Successfully submitted revised manuscript for final acceptance
- Updated memory bank

\begin{center}
\textbf{\large Cover Letter for Revised Manuscript Submission}
\end{center}

@@

We are pleased to submit the revised version of our manuscript entitled ``A Loop Quantum Gravity Inspired Action for the Bosonic String and Emergent Dimensions at Large Scales'' (Reference Number: AOP 81029) for publication in Annals of Physics.

We have carefully addressed all comments and suggestions from the reviewers. A detailed point-by-point response is provided in the accompanying file ``response-to-referee.pdf''.

\textbf{Author Name Change:} One co-author has requested a name change from Luigi Teixeira de Sousa to Lin Teixeira de Sousa. We have contacted namechange@elsevier.com per Elsevier's inclusive author name change policy. This correction does not affect authorship contributions or order.

\textbf{Summary of Revisions:} Major improvements include: (1) Enhanced theoretical foundation with extensive discussions connecting our minimal area approach to existing minimal length proposals in string theory; (2) Clearer physical justification for the expansion parameter $k \ll 1$ and strengthened analogy with T/S-dualities; (3) Clarified anomaly-freedom claims, explaining this refers specifically to absence of central charge anomalies due to finite mode truncation; (4) Added important caveats about approach limitations; (5) Improved interpretation of emergent dimensions and their connection to holographic principles and cosmological horizon scale.

@@

We thank the reviewers for their constructive feedback and look forward to your favorable consideration.

@@

\noindent
\textbf{Attachments:} \texttt{response-to-referee.pdf} (detailed response), \texttt{resubmit-cover-letter.pdf} (cover letter), \texttt{lqg-strings.pdf} (revised manuscript), \texttt{lqg-strings-diff.pdf} (diff file), \texttt{lqg-strings.bib} \& \texttt{lqg-strings.bbl} (bibliography files).

>>>>

\begin{center}
\textbf{\large Cover Letter for 2nd Manuscript Revision}
\end{center}

@@

We thank you for your provisional acceptance of our paper in your esteemed journal.

We have carefully addressed all comments and suggestions from the second round of referee comments. A detailed point-by-point response is provided in the accompanying file ``response-to-referee-r2.pdf''. We hope that we have satisfactorily addresses any concerns the referee might have had.

@@

We thank the referee and the editor once again for their patient and constructive feedback through this process.

@@

\noindent
\textbf{Attachments:} \texttt{response-to-referee-r2.pdf} (detailed response), \texttt{resubmit-cover-letter-r2.pdf} (cover letter), \texttt{lqg-strings.pdf} (revised manuscript).

### 2025-09-07 lqg-strings.tex
Complete T4: Submit final AOP manuscript revisions
- Enhanced Kalb-Ramond field derivation with step-by-step exposition
- Fixed equation label references for improved clarity
- Addressed all referee clarifications in response document
- Successfully submitted revised manuscript for final acceptance
- Updated memory bank

\graphicspath{{figures/}}

@@

\begin{equation} \label{eqn:h=SgS}

@@

\begin{equation} \label{eqn:S=sigma_y}

@@

\begin{equation} \label{eqn:H=1/(2g)G}
	H_{\mu \nu} = \frac{f^{(G)}}{f^{(H)}} \frac{\Delta}{2 g} G_{\mu \nu} .

@@

If we impose the conditions \eqref{eqn:h=SgS}, \eqref{eqn:S=sigma_y} and \eqref{eqn:H=1/(2g)G} plus $T' = - T k / 2$ in the interactionless bimetric Polyakov action \eqref{eqn:polyakov-bimetric}, we obtain the Polyakov version of the area-corrected action \eqref{eqn:modified-ng-action}:

@@

We start from the action in \eqref{eqn:area-corrected-K-R-action-v2} which describes the area-corrected string coupled to the Kalb-Ramond field, since this is the most generic and complete 2-dimensional action with worldsheet diffeomorphism invariance and bulk global Lorentz symmetry, with the correction to the worldsheet geometry due to quantum geometry proposed by our central dogma. The Levi-Civita tensor $\varepsilon ^{a b}$ has been written in terms of the quantum of area 2-form $\Delta _{a b}$ by dividing and multiplying by $\sqrt{\Delta}$. Varying this action \wrt \ $\Delta ^{c d}$ yields
\begin{multline} \label{eqn:var-act-AC-KR}
	\frac{\delta S}{\delta \Delta ^{c d}} = - \frac{1}{4 \pi \alpha '} \Bigg( - \frac{1}{2} \frac{k}{\sqrt{- g}} \Delta \Delta _{c d} \bigg( g^{a b} \del _{a} X^{\mu} \del _{b} X^{\nu} G_{\mu \nu} - \\
	- \sqrt{\Delta} \Delta ^{a b} \del _{a} X^{\mu} \del _{b} X^{\nu} B_{\mu \nu} \bigg) - \\
	- \bigg( \sqrt{- g} - \frac{1}{2} \frac{k \Delta}{\sqrt{- g}} \bigg) \bigg( \frac{1}{2} \sqrt{\Delta} \Delta _{c d} \Delta ^{a b} \del _{a} X^{\mu} \del _{b} X^{\nu} B_{\mu \nu} + \\
	+ \sqrt{\Delta} \delta ^{a} _{c} \delta ^{b} _{d} \del _{a} X^{\mu} \del _{b} X^{\nu} B_{\mu \nu} \bigg) \Bigg) ,
\end{multline}
which when required to vanish can be rearranged into
\begin{multline} \label{eqn:eqn:var-act-AC-KR-rear}
	\Delta _{c d} \Bigg( \frac{k \sqrt{\Delta}}{2} g^{a b} \del _{a} X^{\mu} \del _{b} X^{\nu} G_{\mu \nu} - \\
	- \bigg( g + \frac{3 k \Delta}{4} \bigg) \Delta ^{a b} \del _{a} X^{\mu} \del _{b} X^{\nu} B_{\mu \nu} \Bigg) - \\
	- \bigg( g + \frac{k \Delta}{2} \bigg) \del _{c} X^{\mu} \del _{d} X^{\nu} B_{\mu \nu} = 0 .
\end{multline}
From here, the quantum of area field $\Delta _{c d}$ can be directly related to the pullback of the Kalb-Ramond 2-form $\del _{c} X^{\mu} \del _{d} X^{\nu} B_{\mu \nu}$ as in
\begin{equation} \label{eqn:QA-pullKR}
	\Delta _{c d} = \widetilde{f} \del _{c} X^{\mu} \del _{d} X^{\nu} B_{\mu \nu} ,
\end{equation}
where the function $\widetilde{f}$ is given by a contribution from the pullback of the metric and from the Kalb-Ramond field
\begin{multline} \label{eqn:1/f-KR}
	\frac{1}{\widetilde{f}} = \frac{1}{g + \dfrac{k \Delta}{2}} \Bigg( \frac{k \Delta}{2} g^{a b} \del _{a} X^{\mu} \del _{b} X^{\nu} G_{\mu \nu} - \\
	- \bigg( g + \frac{3 k \Delta}{4} \bigg) \Delta ^{a b} \del _{a} X^{\mu} \del _{b} X^{\nu} B_{\mu \nu} \Bigg) .
\end{multline}
When the equation of motion for the metric $g_{a b}$ is satisfied i.e if $g_{a b} = \del _{a} X^{\mu} \del _{b} X^{\nu} G_{\mu \nu}$, then \eqref{eqn:1/f-KR} simplifies to
\begin{equation} \label{eqn:1/f-KR-simp}
	\frac{1}{\widetilde{f}} = - \frac{k \sqrt{\Delta}}{g + k \Delta}
\end{equation}
or alternatively
\begin{equation} \label{eqn:f-KR-simp}
	\widetilde{f} = - \frac{g + k \Delta}{k \sqrt{\Delta}} = - \sqrt{\Delta} \left( \frac{g}{k \Delta} + 1 \right) .
\end{equation}
Finally, we can then write the quantum of area 2-form $\Delta _{a b}$ in terms of the pullback of the Kalb-Ramond field $b_{a b} = \del _{a} X^{\mu} \del _{b} X^{\nu} B_{\mu \nu}$ as
\begin{equation} \label{eqn:QA-KR-fin}
	\Delta _{a b} = - \sqrt{\Delta} \left( \frac{g}{k \Delta} + 1 \right) b_{a b} .
\end{equation}

>>>>

% \graphicspath{{figures/}}

@@

\begin{equation} \label{eqn:h-delta-relation}

@@

\begin{equation} \label{eqn:delta-epsilon-relation}

@@

\begin{equation} \label{eqn:H-G-relation}
	H_{\mu \nu} = \frac{\Delta}{2 g} G_{\mu \nu} .

@@

If we impose the conditions \eqref{eqn:h-delta-relation}, \eqref{eqn:delta-epsilon-relation} and \eqref{eqn:H-G-relation} plus $T' = - T k / 2$ in the interactionless bimetric Polyakov action \eqref{eqn:polyakov-bimetric}, we obtain the Polyakov version of the area-corrected action \eqref{eqn:modified-ng-action}:

@@

To see how the area 2-form $\Delta _{ab}$ is related to the Kalb-Ramond field we have to go back to \autoref{sec:ws-kalb-ramond} where we looked at the case of the bimetric string action \eqref{eqn:polyakov-bimetric}. We saw that the bimetric Polyakov action can be expressed, quite obviously, as a bimetric Nambu-Goto action \eqref{eqn:double-ng-action}, which we reproduce below for convenience:
\begin{equation}
	S = - T \int \diff ^2 x \sqrt{- g} - T' \int \diff ^2 x \sqrt{- h}.
\end{equation}
From here if we make the mapping $T' = - T k / 2$ and $h = \Delta ^2 / g$, we recover the Nambu-Goto area-corrected action \eqref{eqn:modified-ng-action}
\begin{equation}
	S = - T \int \diff ^2 x \left( \sqrt{- g} - \frac{1}{2} \frac{k \Delta}{\sqrt{- g}} \right) .
\end{equation}
Now, as noted in the main text, the condition $h = \Delta^2/g$ can be achieved if the following holds true \eqref{eqn:h-delta-relation}:
\begin{equation*}
	h_{ab} = \Delta_{ac} \Delta_{bd} g^{cd},
\end{equation*}
where $g^{cd}$ is the inverse of $g_{ab}$. Now, let us assume that $\Delta_{ab}$ can be written as \eqref{eqn:delta-epsilon-relation}:
\begin{equation*}
	\Delta_{ab} = \sqrt{\Delta} \epsilon_{ab}.
\end{equation*}
Now, we recall that the inverse of a $2\times 2$ matrix can be written using the total-antisymmetric symbol as:
\begin{equation}
	g^{ab} = \frac{1}{2g} \epsilon^{ac} \epsilon^{bd} g_{cd},
\end{equation}
where $g = \det{g_{ab}}$. Inserting this identity into \eqref{eqn:h-delta-relation}, and using the expression for the the determinant of a matrix in terms of product of epsilon symbols:
\begin{equation*}
	g = \det{g_{ab}} = \onehalf \epsilon^{ac} \epsilon^{bd} g_{cd},
\end{equation*}
we find that $h = \Delta^2/g$, where $\Delta = \det{\Delta_{ab}}$. What this tells us is that it is natural to identify $\Delta_{ab}$ with the totally anti-symmetric tensor on the worldsheet. Now a two-dimensional manifold can only have one, upto conformal transformations, anti-symmetric tensor and if we require that this tensor be derived from the embedding of the string into the ambient manifold then it makes sense that one should identify $\Delta_{ab}$ with the pullback to the worldsheet of the bulk Kalb-Ramond field $B_{\mu\nu}$.

For a more formal derivation of this fact we start from the action in \eqref{eqn:area-corrected-K-R-action-v2} which describes the area-corrected string coupled to the Kalb-Ramond field, where the Levi-Civita tensor $\varepsilon ^{a b}$ has been written in terms of the quantum of area 2-form $\Delta _{a b}$ by dividing and multiplying by $\sqrt{\Delta}$. Varying this action \wrt \ $\Delta ^{c d}$ yields
\begin{multline} \label{eqn:var-act-AC-KR}
	\frac{\delta S}{\delta \Delta ^{c d}} = - \frac{1}{4 \pi \alpha '} \Bigg( - \frac{1}{2} \frac{k}{\sqrt{- g}} \Delta \Delta _{c d} \bigg( g^{a b} \del _{a} X^{\mu} \del _{b} X^{\nu} G_{\mu \nu} - \\
	- \sqrt{\Delta} \Delta ^{a b} \del _{a} X^{\mu} \del _{b} X^{\nu} B_{\mu \nu} \bigg) - \\
	- \bigg( \sqrt{- g} - \frac{1}{2} \frac{k \Delta}{\sqrt{- g}} \bigg) \bigg( \frac{1}{2} \sqrt{\Delta} \Delta _{c d} \Delta ^{a b} \del _{a} X^{\mu} \del _{b} X^{\nu} B_{\mu \nu} + \\
	+ \sqrt{\Delta} \delta ^{a} _{c} \delta ^{b} _{d} \del _{a} X^{\mu} \del _{b} X^{\nu} B_{\mu \nu} \bigg) \Bigg) ,
\end{multline}
which when required to vanish can be rearranged into
\begin{multline} \label{eqn:eqn:var-act-AC-KR-rear}
	\Delta _{c d} \Bigg( \frac{k \sqrt{\Delta}}{2} g^{a b} \del _{a} X^{\mu} \del _{b} X^{\nu} G_{\mu \nu} - \\
	- \bigg( g + \frac{3 k \Delta}{4} \bigg) \Delta ^{a b} \del _{a} X^{\mu} \del _{b} X^{\nu} B_{\mu \nu} \Bigg) - \\
	- \bigg( g + \frac{k \Delta}{2} \bigg) \del _{c} X^{\mu} \del _{d} X^{\nu} B_{\mu \nu} = 0 .
\end{multline}
From here, the quantum of area field $\Delta _{c d}$ can be directly related to the pullback of the Kalb-Ramond 2-form $\del _{c} X^{\mu} \del _{d} X^{\nu} B_{\mu \nu}$ as in
\begin{equation} \label{eqn:QA-pullKR}
	\Delta _{c d} = \widetilde{f} \del _{c} X^{\mu} \del _{d} X^{\nu} B_{\mu \nu} ,
\end{equation}
where the function $\widetilde{f}$ is given by a contribution from the pullback of the metric and from the Kalb-Ramond field
\begin{multline} \label{eqn:1/f-KR}
	\frac{1}{\widetilde{f}} = \frac{1}{g + \dfrac{k \Delta}{2}} \Bigg( \frac{k \Delta}{2} g^{a b} \del _{a} X^{\mu} \del _{b} X^{\nu} G_{\mu \nu} - \\
	- \bigg( g + \frac{3 k \Delta}{4} \bigg) \Delta ^{a b} \del _{a} X^{\mu} \del _{b} X^{\nu} B_{\mu \nu} \Bigg) .
\end{multline}
When the equation of motion for the metric $g_{a b}$ is satisfied i.e if $g_{a b} = \del _{a} X^{\mu} \del _{b} X^{\nu} G_{\mu \nu}$, then \eqref{eqn:1/f-KR} simplifies to
\begin{equation} \label{eqn:1/f-KR-simp}
	\frac{1}{\widetilde{f}} = - \frac{k \sqrt{\Delta}}{g + k \Delta}
\end{equation}
or alternatively
\begin{equation} \label{eqn:f-KR-simp}
	\widetilde{f} = - \frac{g + k \Delta}{k \sqrt{\Delta}} = - \sqrt{\Delta} \left( \frac{g}{k \Delta} + 1 \right) .
\end{equation}
Finally, we can then write the quantum of area 2-form $\Delta _{a b}$ in terms of the pullback of the Kalb-Ramond field $b_{a b} = \del _{a} X^{\mu} \del _{b} X^{\nu} B_{\mu \nu}$ as
\begin{equation} \label{eqn:QA-KR-fin}
	\Delta _{a b} = - \sqrt{\Delta} \left( \frac{g}{k \Delta} + 1 \right) b_{a b} .
\end{equation}
